---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Sepideh AhmadiTalei"
date: "September 28, 2023"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r load-pkg}

install.packages("magrittr")
install.packages("tidyverse")
install.packages("tidymodels")
install.packages("gt")
install.packages("gtExtras")
install.packages("DataExplorer")

library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
```

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

## Exercises

### Exercise 1

```{r Summarize data}
the_tate |>
  dplyr::summarize(
    artist = length(unique(artist)),  
    min_year = min(year, na.rm = TRUE), 
    max_year = max(year, na.rm = TRUE),
    min_acquisitionYear = min(acquisitionYear, na.rm = TRUE),  
    max_acquisitionYear = max(acquisitionYear, na.rm = TRUE),  
  )
```

The `the_tate` dataset has \_*3336*\_ unique artists who worked from \_*1545*\_ to \_*2012*\_. The works were acquired between the years \_*1823*\_ and \_*2013*\_.

### Exercise 2

```{r Missing data}
the_tate |>
  DataExplorer::introduce()
```

```{r}
the_tate |>
  DataExplorer::plot_missing()
```

```{r}
the_tate |>
  dplyr::filter(is.na(year)) |>
  dplyr::distinct(artist)
```

```{r}
the_tate |>
  dplyr::filter(is.na(year)) |>
  dplyr::distinct(title)
```

How number of works with missing dates is \_\_.

The number of artists whose works have missing dates is \_\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_\_\_\_.

### Exercise 3

```{r Ordering artists by number of works}
the_tate |>
  dplyr::group_by(artist) |>
  dplyr::mutate(number_of_works=n()) |>
  dplyr::select(artist,number_of_works) |>
  dplyr::arrange(desc(n)) |>
  dplyr::distinct() |>
  dplyr::ungroup() |>
  dplyr::slice(c(1,10)
  )
```

The artist with the most works in the Tate collection is \_*Turner, Joseph Mallord*\_.

The artist with the tenth-most works in the Tate collection is \_*Warhol, Andy*\_.

### Exercise 4

```{r}
the_tate |>
  dplyr::group_by(artist) |>
  dplyr::mutate(number_of_works=n()) |>
  dplyr::select(artist,number_of_works) |>
  dplyr::arrange(desc(n)) |>
  dplyr::distinct() |>
  dplyr::ungroup() |>
  dplyr::slice(c(1,10)
  )
```

The artist with the greatest number of works in the Tate collection represent \_\_\_% of the total number of works

### Exercise 5

There are \_\_ duplicate artist-title pairs

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
